PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-03-24 txt/manuscript.tex
Fix last bibitem
bibliografia
biblio

\bibitem{preskill} Preskill, J. Quantum Computing in the NISQ era and beyond. Quantum 2 (2018): 79.

@@

\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. Strategies for

@@

98.4 (2018): 042103.
\bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge university press.

@@

\bibitem{watrous2021simplier} Watrous, J. (2012). Simpler semidefinite programs for completely bounded norms. arXiv preprint arXiv:1207.5726.

@@

\bibitem{benedetti2018generative} BBenedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y.,  Perdomo-Ortiz, A. (2019). A generative modeling approach for benchmarking and training shallow quantum circuits. Quantum Information, 5(1), 45.

>>>>

\bibitem{preskill} Preskill, J. (2018). Quantum Computing in the NISQ era and beyond. Quantum 2, 79.

@@

\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. (2018). Strategies for

@@

98.4, 042103.
\bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge University Press.

@@

\bibitem{watrous2021simplier} Watrous, J. (2013). Simpler semidefinite programs for completely bounded norms. Chicago Journal of Theoretical Computer Science, 8.

@@

\bibitem{benedetti2018generative} Benedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y., Perdomo-Ortiz, A. (2019). A generative modeling approach for benchmarking and training shallow quantum circuits. npj Quantum Information, 5(1), 45.
